\documentclass[letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{url}
\usepackage{hanging}
\usepackage{parskip}
\usepackage[compact]{titlesec}
\usepackage[warn]{textcomp}
\usepackage{pifont}
\usepackage{natbib, bibentry}
\makeatletter\let\saved@bibitem\@bibitem\makeatother

\usepackage{hyperref}
\makeatletter\let\@bibitem\saved@bibitem\makeatother

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
%\usepackage[T1]{fontenc}
%\usepackage[sc,osf]{mathpazo}

\pagestyle{empty}

% Set your name here
\def\name{Dr Yang Wang}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}
\hypersetup{pdfstartview={XYZ null null 1.00}}

\geometry{
%  body={6.5in, 8.5in},
  left=0.35in,
  right =0.4in,
  top=0.3in,
  bottom=0.3in,
}

% Customize page headers
%\pagestyle{myheadings}
%\markright{\name}
%\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\bfseries\large}
%\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
%\renewenvironment{itemize}{
%  \begin{list}{}{
%    \setlength{\leftmargin}{1.5em}
%  }
%}{
%  \end{list}
%}
\renewcommand{\labelitemii}{\ding{226}}

\begin{document}

% Place name at left
%{\huge \name}

% Alternatively, print name centered and bold:
\centerline{\LARGE \bf Dr Yang Wang}
\vspace{0.05in}
\centerline{\large Senior Modelling Consultant – Application}

\begin{minipage}{\linewidth}
%\href{http://*}{}
\begin{center}
Email: \href{mailto:yang.wang@es.catapult.org.uk}{\tt yang.wang@es.catapult.org.uk} , Tel: 07784670342 \\
\end{center}
\end{minipage}

\rule{\textwidth}{1pt}
%\ul{\Huge\textbf{Some text\mbox{\hspace{1in}}}}

\section*{Interests}
\begin{itemize}
\item Whole energy system modelling and optimisation for Net Zero transition
\item Strategic energy planning and stakeholder engagement
\item Innovation in sustainable energy technologies, including the potential of AI and data-driven methods
\end{itemize}

\section*{Key Skills}
\begin{itemize}
\item Strategic energy planning tool development and deployment
\item Advanced numerical methods and modelling with performance optimizations
\item Data analysis, scenario modelling, and machine learning applications
\item Programming: Python, MATLAB/SIMULINK, Fortran; Version control tools (Git, SVN, Mercurial)
\item Technical leadership, project delivery, mentoring, and training facilitation
\item Business development, stakeholder engagement, and cross-functional collaboration
\item Problem-solving and innovation in complex technical systems
\end{itemize}

\section*{Education}
\begin{itemize}
  \item 2012 - 2016 \hspace{2pt} PhD in Mechanical Engineering, Queen Mary, University of London, United Kingdom
  \item 2009 - 2012 \hspace{2pt} MSc in Power Engineering and Thermophysics, Xi’an Jiaotong University, China
  \item 2005 - 2009 \hspace{2pt} BEng in Energy and Power Engineering, Xi’an Jiaotong University, China
\end{itemize}

\section*{Work Experience and Achievements}
\begin{itemize}
\item Jan 2021 - present \hspace{2pt} Senior Modelling Analyst at Energy Systems Catapult, Birmingham, United Kingdom
  \begin{itemize}
    \item Led development, deployment, and interpretation of strategic energy planning tools (ESME, ESME-Flex, EPN, LAEPForward) for national and local energy system modelling across multiple LAEP projects.
    \item Provided technical leadership and mentoring to project teams, delivering high-impact projects (ITEG, LAEPs, Cogen, EFM, ITNZ3) supporting Net Zero strategies.
    \item Interpreted and communicated complex modelling outputs to inform strategic decision-making for clients and stakeholders.
    \item Developed and delivered training sessions showcasing energy system modelling tools' impact in real-world projects.
    \item Promoted ESME tools and Net Zero Market Data through marketing collaborations, producing promotional content and driving adoption across teams.
    \item Advanced AI tool adoption by sharing best practices and enhancing team productivity through technology innovation.
    \item Supported business development through academic partnerships with Warwick Energy Innovation Centre, King's College London, etc.
    \item Fostered inclusive workplace practices through collaboration with EDI advocates and promoting effective cross-disciplinary teamwork.
  \end{itemize}
\item Oct 2019 - Dec 2020 \hspace{2pt} CFD Software Engineer (solver developer) at Advanced Design Technology, London, United Kingdom
   \begin{itemize}
   \item Contributed to the development of high-performance CFD solvers (TDShaper and TD1), improving simulation accuracy and efficiency for turbo-machinery design.
   \item Successfully improved CFD solver convergence rates from 0\% to 80\% through numerical method enhancements and solver optimization, enabling previously intractable turbo-machinery simulations to be solved.
   \item Speeded up CPU time by 50\% on test cases.
   \item Collaborated with cross-functional teams to deliver software updates on schedule.
   \end{itemize}
\item Dec 2018 - Sep 2019 \hspace{2pt} Flight Data Analyst at Altaeros (MIT spin-out), Somerville, Massachusetts, United States
  \begin{itemize}
  \item Analyzed flight data to support development and optimization of airborne wind energy systems.
  \item Mentored junior mechanical engineers on modelling design strategies.
  \item Provided actionable insights to engineering teams, contributing to successful test campaigns and system improvements.
  \end{itemize}
	
\item Nov 2017 - Dec 2018 \hspace{2pt} Parenting and working from home during relocation, Cambridge, USA
		\begin{itemize}
% 		\item Studying data types/structures and algorithms in C++
% 		\item Researching on multi-physics modelling and computation strategies
		\item Completed Stanford University Machine Learning course on Coursera.
		\item Maintained and developed technical skills during career break.
		\end{itemize}		
\item Mar 2017 - Oct 2017  \hspace{2pt} Research fellow on projects funded by Engineering and Physical Science Research Council (EPSRC), School of Engineering, University of Warwick, Coventry, United Kingdom
		\begin{itemize}
		\item Contributed to research on next-generation grid-scale thermal energy storage and ultra-supercritical steam power generation technologies.
		\item Mentored junior researchers on fluid/thermo dynamics modelling and numerical methods.
    \item Published research findings in peer-reviewed journals and presented at conferences.
		\end{itemize}

\item Sep 2012 - Jan 2017  \hspace{2pt} PhD in Mechanical Engineering, Queen Mary University of London, United Kingdom
		\begin{itemize}
		\item Led development team of in-house CFD codes (Fortran) for incompressible flow with discrete adjoint sensitivity/gradient solvers using Automatic Differentiation.
		\item Successfully delivered project milestones for European Commission-funded \textsl{About Flow} project and contributed to multiple peer-reviewed publications.
		\end{itemize}
		
\item Sep 2009 - Jul 2012  \hspace{2pt} MSc Research Project, Xi'an Jiaotong University, China
  \begin{itemize}
  \item Developed spectral element method for acoustic propagation in non-uniform flows, contributing to computational fluid dynamics research.
  \item Implemented numerical algorithms and validated results against analytical solutions.
  \end{itemize}

\item Sep 2008 - Jun 2009  \hspace{2pt} BEng Final Project, Xi'an Jiaotong University, China
  \begin{itemize}
  \item Designed high flow rate vortex/generative blower system for industrial applications.
  \item Conducted performance analysis and optimization of blower design parameters.
  \end{itemize}
		
\end{itemize}

\section*{Selected Publications}
Please visit \href{https://raw.githubusercontent.com/guliyolanda/CV/master/YW-papers.pdf} {\tt webpage} for  my publications. 


\end{document}
