\documentclass[letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{url}
\usepackage{hanging}
\usepackage{parskip}
\usepackage[compact]{titlesec}
\usepackage[warn]{textcomp}
\usepackage{pifont}
\usepackage{natbib, bibentry}
\makeatletter\let\saved@bibitem\@bibitem\makeatother

\usepackage{hyperref}
\makeatletter\let\@bibitem\saved@bibitem\makeatother

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
%\usepackage[T1]{fontenc}
%\usepackage[sc,osf]{mathpazo}

\pagestyle{empty}

% Set your name here
\def\name{Yang Wang}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}
\hypersetup{pdfstartview={XYZ null null 1.00}}

\geometry{
%  body={6.5in, 8.5in},
  left=0.5in,
  right =0.5in,
  top=0.5in,
  bottom=0.5in,
}

% Customize page headers
%\pagestyle{myheadings}
%\markright{\name}
%\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\bfseries\large}
%\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
%\renewenvironment{itemize}{
%  \begin{list}{}{
%    \setlength{\leftmargin}{1.5em}
%  }
%}{
%  \end{list}
%}
\renewcommand{\labelitemii}{\ding{226}}

\begin{document}

% Place name at left
%{\huge \name}

% Alternatively, print name centered and bold:
\centerline{\LARGE \bf \name}

%\vspace{0.25in}

\begin{minipage}{\linewidth}
%\href{http://*}{}
\begin{center}
21 Brookline Street, Cambridge, MA, 02139, United States\\
Email: \href{mailto:guliyolanda@gmail.com}{\tt guliyolanda@gmail.com} , Tel: +1(617)7109267 \\
Homepage:  \href{https://guliyolanda.github.io}{\tt https://guliyolanda.github.io} \\
\end{center}
\end{minipage}

\vspace{0pt}
\rule{\textwidth}{1pt}
%\ul{\Huge\textbf{Some text\mbox{\hspace{1in}}}}

\vspace{-12pt}
\section*{Research Interests}
\vspace{-10pt}
\begin{itemize}
\item Computational Aided Engineering (CAE)
\item Computational Fluid Dynamics (CFD) in multi-disciplinary applications
\item Computational Aero-Acoustics (CAA)
\item CAD/Node-based shape deformation and gradient-based optimisation
\item Numerical modeling and optimization
\end{itemize} 

\vspace{-12pt}
\section*{Skills}
\vspace{-10pt}
\begin{itemize}
\item Finite Volume Method and Spectral Element Method
\item Numerical methods for Partial Differential Equations: algorithms, discretisation schemes and linear solvers
\item Fortran, MATLAB/Octave and C++ programming
%\item Chemical Engineering process/system simulation tool: Aspen Plus
\item Tools/software: SolidWorks, ProE, GMSH, ICEM, ParaView, OpenFOAM, Fluent
\item Automatic Differentiation (AD) tool TAPENADE
\item Linux operation systems, Vim, Meld, Make, Git, Doxygen, Gprof, and HYPRE open source libraries 
\end{itemize}

\vspace{-12pt}
\section*{Education}
\vspace{-10pt}
\begin{itemize}
  \item 2012. 9 - 2017. 1 \hspace{2pt} PhD in Mechanical Engineering, Queen Mary, University of London, United Kingdom
  \item 2009. 9 - 2012. 6 \hspace{2pt} MSc in Power Engineering and Thermophysics, Xi’an Jiaotong University, China
  \item 2005. 9 - 2009. 7 \hspace{2pt} BEng in Energy and Power Engineering, Xi’an Jiaotong University, China
\end{itemize}

\vspace{-12pt}
\section*{Academic experience}
\vspace{-10pt}
\begin{itemize}
\item 2017. 11 - present \hspace{2pt} Parenting and working from home during relocation, Cambridge, USA
		\begin{itemize}
		\item Mass/species transportation coupling with standard CFD flow solvers
		\item	Journal papers writing and revision; paper reviewing work invited by journal editors
		\end{itemize}		
\item 2017. 3 - 2017. 10  \hspace{2pt} Research fellow on projects funded by Engineering and Physical Science Research Council (EPSRC), School of Engineering, University of Warwick, Coventry, United Kingdom
		\begin{itemize}
		\item	Next Generation Grid Scale Thermal Energy Storage Technologies: Novel system design for Compressed Air Energy Storage (CAES) coupled with Reverse Osmosis (RO) water producing process
		\item	Ultra-Supercritical (USC) steam power generation technology with Circulating Fluidized Bed (CFB): Combustion, Materials and Modelling: Heat transfer numerical model of CFB boiler integrated with water-wall heat exchange
		\end{itemize}

\item 2012. 9 - 2017. 1  \hspace{2pt} PhD candidate working on the project \textit{About Flow} funded by the European commission
		\begin{itemize}
		\item Development of integrated CFD and adjoint sensitivity solvers
		\item Solver development on cell-centered/face-based and node-centered/edge-based data structure
		\item	SIMPLE-like algorithms vs. Pressure Schur Complement (PSC) method theatrical derivation
		\item	Automatic Differentiation (AD) for CFD code based on source transformation (TAPENADE)		
		\item	CAD-based (NURBS surfaces) shape optimization with mesh deformation based on linear elasticity theory
		\item	Fluid dynamics analysis on air duct cases in Volkswagen Golf vehicle
		\item	Membrane process modeling and governing equations implementation
		\item	Fluid dynamics combined with filaments surface sensitivity analysis on spacers design in membrane channel
		\end{itemize}
		
\item 2009. 9 - 2012. 6  \hspace{2pt} Master Thesis: Study of spectral element method for acoustic propagation problem in non-uniform flows
		\begin{itemize}
		\item	The numerical model of acoustic propagation derivation for non-uniform flow
		\item	Implementation of group velocity method with high accuracy on the absorbing boundary conditions
		\end{itemize}

\item 2008. 9 - 2009. 6  \hspace{2pt} Bachelor thesis: The design of vortex blower working on high flow rate
		\begin{itemize}
		\item High flow rate vortex blower design and 3D model via software ProE
		\end{itemize}
		
\end{itemize}

\vspace{-12pt}
\section*{Selected Publications}
\vspace{-10pt}

%\printbibliography[env=numbered+bold, heading=none, sorting=ynt, resetnumbers=true]

\nobibliography{publications_yw, abbrev}
\bibliographystyle{abbrv}

\begin{enumerate}
\item \bibentry{wang18stablisation}
\item \bibentry{wang2018}
\item \bibentry{wang18CAES}
\item \bibentry{wang2016computational}
\item \bibentry{zhang2016geometric}
\item \bibentry{he2016evaluation}
\item \bibentry{geng2016research}
\item \bibentry{akbarzadeh2015fixed}
\item \bibentry{wang2015stabilisation}
\item \bibentry{he2015maximum}
\item \bibentry{he2015stand}

%\item \bibentry{}
\end{enumerate}


\vspace{-12pt}
\section*{Awards and grants}
\vspace{-10pt}
\begin{itemize}
\item 2015 Postgraduate Research Fund from QMUL
\item 2014 Student grant from SEMS
\item 2012 Best Graduates (Top 10\%)
\item 2010 Outstanding Postgraduate Student Award (Top 15\%)
\item 2009 Postgraduate Innovation Fund Scholarship (1st Class, 2/46)
\item 2009 Best Graduates (Top 10\%)
\item 2008 \textit{Fusheng} Scholarship (1st Class, Top 15\%)
\end{itemize}

\vspace{-12pt}
\section*{Teaching and supervising experiences}
\vspace{-10pt}

\begin{itemize}
\item	2012 - 2015  \hspace{2pt} Demonstrating in modules:
		\begin{itemize}
		\item	Heat transfer and Fluid Mechanics: teaching assistant
		\item	Mechanics of Fluids: experiment demonstration and report marking
		\item	Computer Aided Engineering in Fluids and Solids: OpenFOAM tutorial
		\end{itemize}

\item	2009 - 2012  \hspace{2pt} Instructor of Class 2009 in Department of Fluid Machinery
\end{itemize}

% Footer
%\begin{center}
%  \begin{footnotesize}
%    Last updated: \today \\
%  \end{footnotesize}
%\end{center}

\end{document}
